comgen-outline

### 2017-12-16 paper/case1-generics.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

\begin{figure}
\centering
    \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf}
    \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities. Left: Participants first generated animal names after seeing six example categories. Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.}
    \label{fig:generics-prior-task}
\end{figure}

@@

The fixed-threshold model is a lesioned version of the unceratin-threshold model: It has access to the full prior distribution on feature-probabilities $P(h)$ and models endorsement as an information-theoretic decision of producing the generic vs. an alternative.
The only difference is that this model uses a fixed-threshold as the core meaning of a generic statement, rather than an uncertain threshold.
For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
  Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further   specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
]
This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.

@@

model_prefix <- "results-generics-jointModel-S1-smntcs_"

# m.samp <- data.frame()
# m.samp.fixed <- data.frame()
# for (i in seq(1, n_chains)){
#   mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))
#   
#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", model_prefix,"some-",
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
#   }
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.samp.fixed,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

m.gen.somemodel.endorsement <- m.samp.fixed %>%
  filter(type == 'endorsement') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

#model_prefix <- "results-generics-jointModel-10bins-S1-smntcs_"

#m.samp <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
                     #20000, "_burn", 10000, "_lag", 20, "_chain", 2, ".csv", sep = ""))
#m.samp <- fread("~/Documents/research/communicating-generalizations/models/generics/results/results-fullModel-s1-allowUPriors-refinedPriors-fixedNull-prevPriorFactorBugFixed-smtncsgeneric-100000_burn100000_chain1.csv")

m.gen.fullmodel.endorsement <- m.samp %>%
 # filter(type == 'endorsement', param == 'generic') %>%
  #filter(type == 'predictive', param == 'generic') %>%
  filter(type == 'endorsement') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.endorse.rsa <- bind_rows(
  left_join(
    d.gen.endorse.bayes,
    m.gen.fullmodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.gen.endorse.bayes,
    m.gen.somemodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "some_model")
)

>>>>

```{r generics-prior-task, fig.cap:"Test"}
fig.priors.expt <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-bothStages.pdf", sep=""), scale = 1)
fig.priors.expt
```

<!-- \begin{figure} -->
<!-- \centering -->
<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-bothStages.pdf} -->
<!--     \caption{Design of Experiment 1b for eliciting prior knowledge about feature-probabilities. Left: Participants first generated animal names after seeing six example categories. Right: One feature at a time, participants estimated the percentage of the category with the feature, for each category.} -->
<!--     \label{fig:generics-prior-task} -->
<!-- \end{figure} -->

@@

The fixed-threshold model is a lesioned version of the unceratin-threshold model: It models endorsement as an information-theoretic decision of producing the generic vs. an alternative, and has access to the full prior distribution on feature-probabilities $P(h)$. 
The only difference is that this model uses a fixed-threshold as the core meaning of a generic statement, rather than an uncertain threshold.
For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).

^[
  Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further   specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
]
This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.

@@

model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-"
# m.samp <- data.frame()
# m.samp.fixed <- data.frame()
#for (i in seq(1, n_chains)){
  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
# }
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.samp.fixed,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
load(file = paste(project.path, "models/generics/results/results-generics-jointModel-S1-some-inferFixedThreshold-noise-100000_burn50000_lag20_2chains.RData", sep = ""))

# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
# 
# m.samp.fixed <- fread(paste(project.path,  "models/generics/results/", "results-generics-jointModel-wNoise-inferFixedThreshold-20bins-S1-smntcs_some-100000_burn50000_lag20_chain1.csv", sep = ""))
# 
# tail(m.samp.fixed)

fixed.params.posterior <-  m.samp.fixed %>% 
  filter(param %in% c("noise", "fixedThreshold")) %>%
  group_by(param) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.somemodel.endorsement <- m.samp.fixed %>%
  filter(type == 'endorsement', param == "some") %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

# m.gen.fullmodel.endorsement <- m.samp.samp %>%
#   rename(type = Parameter, property = Property, category = Category, val = Value, param = Extra) %>%
#   group_by(type, property, category, param) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

m.gen.fullmodel.endorsement <- m.samp %>%
 filter(type == 'endorsement', param == 'generic') %>%
  # filter(type == 'predictive', param == 'generic') %>%
 # filter(type == 'endorsement') %>%
  group_by(type, param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```

```{r generic-model-scatters}
m.gen.endorse.rsa <- bind_rows(
  left_join(
    d.gen.endorse.bayes,
    m.gen.fullmodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "generics_model"),
  left_join(
    d.gen.endorse.bayes,
    m.gen.somemodel.endorsement %>%
      mutate(sentence = paste(category, " ", property, ".", sep = "")) %>%
      ungroup() %>%
      select(-type, -param)
  ) %>%
    mutate(src = "some_model")
)

### 2017-12-16 paper/case2-habituals.Rmd
refactor fig1, start to remake gen priors task fig, some edits to causals

# for (i in seq(1, n_chains)){
#   mi <- fread(paste(project.path,  "models/habituals/results/",
#                     model_prefix, "smtncs_habitual-",
#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
# 
#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
#                     model_prefix, "smtncs_some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
# 
# }
# 
# save(m.hab.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.hab.fixed.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "some_model",
                                      "habituals_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Speaker model - fixed semantics",
                                 "Speaker model - uncertain semantics",
                                 "Referent frequency alone", "Distinctiveness + referent frequency"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")+
  guides(fill = F)
```

>>>>

for (i in seq(1, n_chains)){
  # mi <- fread(paste(project.path,  "models/habituals/results/",
  #                   model_prefix, "smtncs_habitual-",
  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))

  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
  #                   model_prefix, "smtncs_some-",
  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
  #                         "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
  # 
  #m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
}

# save(m.hab.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.hab.fixed.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# save(m.hab.fixed.samp,
#      file = paste(project.path,  "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

@@

# load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
load(paste(project.path,  
           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

# m.hab.fixed.samp <- fread(paste(project.path,  "models/habituals/results/",
#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain1.csv", sep = ""))

fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
  filter(B %in% c("noise", "fixedThreshold")) %>%
  group_by(B) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "some_model",
                                      "habituals_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Fixed semantics model",
                                 "Uncertain semantics model",
                                 "Referent frequency alone", "Distinctiveness + referent frequency"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")+
  guides(fill = F)
```
